---
title: "yangy22_OriginalHomeworkCode_04"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Problem 1

Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data, using the following guidelines:

Your function should take the following arguments: p1 and n1 (no default) representing the estimated proportion and sample size (i.e., based on your sample data); p2 and n2 (both defaulting to NULL) that contain a second sample’s proportion and sample size data in the event of a two-sample test; p0 (no default) as the expected value for the population proportion; and alternative (default “two.sided”) and conf.level (default 0.95), to be used in the same way as in the function t.test().

Your function should take the following arguments: p1 and n1 (no default) representing the estimated proportion and sample size (i.e., based on your sample data); p2 and n2 (both defaulting to NULL) that contain a second sample’s proportion and sample size data in the event of a two-sample test; p0 (no default) as the expected value for the population proportion; and alternative (default “two.sided”) and conf.level (default 0.95), to be used in the same way as in the function t.test().

When conducting a two-sample test, it should be p1 that is tested as being smaller or larger than p2 when alternative=“less” or alternative=“greater”, the same as in the use of x and y in the function t.test().
The function should perform a one-sample Z-test using p1, n1, and p0 if either p2 or n2 (or both) is NULL.
The function should contain a check for the rules of thumb we have talked about (n∗p>5
 and n∗(1−p)>5
) to ensure the validity of assuming the normal distribution in both the one- and two-sample settings. If this is violated, the function should still complete but it should also print an appropriate warning message.
The function should return a list containing the members Z (the test statistic), P (the appropriate p value), and CI (the two-sided CI with respect to “conf.level” around p1 in the case of a one-sample test and around p2-p1 in the case of a two-sample test). For all test alternatives (“two.sided”, “greater”, “less”), calculate symmetric CIs based on quantiles of the normal distribution rather than worrying about calculating single-limit confidence bounds.
```{r Zprop}

n <- 1000
x <- 20
n2 <- NULL
x2 <-NULL
phat <- x/n  # our estimate of pi
phat

if(n*phat > 5 & n*(1 - phat) > 5) {
  Zprop<- function(p1, p2, n1, n2, alternative = "two.sided", alpha = 0.05) { {
        p1 <- x/n
        n1 <- length(n)
        p2 <- x2/n2
        n2 <- length(n2)
        pstar <- x+x1/n+n1
        if (alternative == "one.tailed") {
            p[i] <- (p1-phat)/sqrt(phat*(1-phat)/n)
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- (p2-p1-phat)/sqrt(pstar*(1-pstar)/(1/n+1/n2))
            }
          
            }
            hyp <- "p2 ≠ p1"
        }
    }


} else {
    Zprop<- function(p1, p2, n1, n2, alternative = "two.tailed", alpha = 0.05,
    k = 1000) {
    p <- rep(NA, k)  # sets up a vector of empty p values
    for (i in 1:k) {
        p1 <- rnorm(n = n, mean = n2, sd = sigma)
        n1 <- length(p1)
        p2 <- NULL
        n2 <- NULL
        p0 <- 0
        if (alternative == "less") {
            p[i] <- pnorm(z, lower.tail = TRUE)  # calculates the associated p value
            hyp <- "p2 < p1"
        }
        if (alternative == "greater") {
            p[i] <- pnorm(z, lower.tail = FALSE)
            hyp <- "p1 > p2"
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- 2 * pnorm(z, lower.tail = FALSE)
            }
            if (z < 0) {
                p[i] <- 2 * pnorm(z, lower.tail = TRUE)
            }
            hyp <- "p2 ≠ p1"
        }
    }
}

  print("Warning distribution not normal")}

```

## Question 2
```{r Question 2, eval=FALSE}
library(curl)
library(ggplot2)
library(tidyverse)

f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)

filter(d, col == "MaxLongevity_m" | col == "Brain_Size_Species_Mean")  %>% 
   na.omit()
h <- df$MaxLongevity_m
w <- df$Brain_Size_Species_Mean
y <- h - mean(h)
x <- w - mean(w)
z <- data.frame(cbind(x, y))
g <- ggplot(data = z, aes(x = x, y = y)) 
g

m <- lm( MaxLongevity_m ~ Brain_Size_Species_Mean , data = df)
m
g <- ggplot(data = d, aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g
```