---
title: "yangy22_OriginalHomeworkCode_04"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Problem 1

Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data, using the following guidelines:

Your function should take the following arguments: p1 and n1 (no default) representing the estimated proportion and sample size (i.e., based on your sample data); p2 and n2 (both defaulting to NULL) that contain a second sample’s proportion and sample size data in the event of a two-sample test; p0 (no default) as the expected value for the population proportion; and alternative (default “two.sided”) and conf.level (default 0.95), to be used in the same way as in the function t.test().
```{r Zprop}
Zprop<- function(mu0, muA, sigma, n, alternative = "two.tailed", alpha = 0.05,
    k = 1000) {
    p <- rep(NA, k)  # sets up a vector of empty p values
    for (i in 1:k) {
        p1 <- rnorm(n = n, mean = muA, sd = sigma)  # draw from Ha
        n1 <- length(x)
        p2 <- NULL
        n2 <- NULL
        p0 <- 
        if (alternative == "less") {
            p[i] <- pnorm(z, lower.tail = TRUE)  # calculates the associated p value
            hyp <- "muA < mu0"
        }
        if (alternative == "greater") {
            p[i] <- pnorm(z, lower.tail = FALSE)
            hyp <- "muA > mu0"
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- 2 * pnorm(z, lower.tail = FALSE)
            }
            if (z < 0) {
                p[i] <- 2 * pnorm(z, lower.tail = TRUE)
            }
            hyp <- "muA ≠ mu0"
        }
    }

    curve(dnorm(x, mu0, sigma/sqrt(n)), mu0 - 4 * sigma/sqrt(n), mu0 + 4 * sigma/sqrt(n),
        main = paste("Sampling Distributions Under the Null (red)\nand Alternative Hypotheses (blue)\nType II error rate from simulation = ",
            length(p[p >= alpha])/k, sep = ""), xlab = "x", ylab = "Pr(x)",
        col = "red", xlim = c(min(c(mu0 - 4 * sigma/sqrt(n), muA - 4 * sigma/sqrt(n))),
            max(c(mu0 + 4 * sigma/sqrt(n), muA + 4 * sigma/sqrt(n)))), ylim = c(0,
            max(c(dnorm(mu0, mu0, sigma/sqrt(n))), dnorm(muA, muA, sigma/sqrt(n)))))

    curve(dnorm(x, muA, sigma/sqrt(n)), muA - 4 * sigma/sqrt(n), muA + 4 * sigma/sqrt(n),
        col = "blue", add = TRUE)
    abline(h = 0)

    if (alternative == "less") {
        polygon(cbind(c(mu0 - qnorm(1 - alpha) * sigma/sqrt(n), seq(from = mu0 -
            qnorm(1 - alpha) * sigma/sqrt(n), to = muA + 4 * sigma/sqrt(n),
            length.out = 100), muA + 4 * sigma/sqrt(n))), c(0, dnorm(seq(mu0 -
            qnorm(1 - alpha) * sigma/sqrt(n), to = muA + 4 * sigma/sqrt(n),
            length.out = 100), mean = muA, sd = sigma/sqrt(n)), 0), border = "black",
            col = "grey")
        abline(v = mu0 - qnorm(1 - alpha) * sigma/sqrt(n), col = "black", lty = 3,
            lwd = 2)
    }

    if (alternative == "greater") {
        polygon(cbind(c(muA - 4 * sigma/sqrt(n), seq(from = muA - 4 * sigma/sqrt(n),
            to = mu0 + qnorm(1 - alpha) * sigma/sqrt(n), length.out = 100),
            mu0 + qnorm(1 - alpha) * sigma/sqrt(n))), c(0, dnorm(seq(from = muA -
            4 * sigma/sqrt(n), to = mu0 + qnorm(1 - alpha) * sigma/sqrt(n),
            length.out = 100), mean = muA, sd = sigma/sqrt(n)), 0), border = "black",
            col = "grey")
        abline(v = mu0 + qnorm(1 - alpha) * sigma/sqrt(n), col = "black", lty = 3,
            lwd = 2)
    }

    if (alternative == "two.tailed") {
        abline(v = mu0 - qnorm(1 - alpha/2) * sigma/sqrt(n), col = "black",
            lty = 3, lwd = 2)
        abline(v = mu0 + qnorm(1 - alpha/2) * sigma/sqrt(n), col = "black",
            lty = 3, lwd = 2)

        if (z > 0) {
            # greater
            polygon(cbind(c(muA - 4 * sigma/sqrt(n), seq(from = muA - 4 * sigma/sqrt(n),
                to = mu0 + qnorm(1 - alpha/2) * sigma/sqrt(n), length.out = 100),
                mu0 + qnorm(1 - alpha/2) * sigma/sqrt(n))), c(0, dnorm(seq(from = muA -
                4 * sigma/sqrt(n), to = mu0 + qnorm(1 - alpha/2) * sigma/sqrt(n),
                length.out = 100), mean = muA, sd = sigma/sqrt(n)), 0), border = "black",
                col = "grey")
        }

        # less
        if (z < 0) {
            polygon(cbind(c(mu0 - qnorm(1 - alpha/2) * sigma/sqrt(n), seq(from = mu0 -
                qnorm(1 - alpha/2) * sigma/sqrt(n), to = muA + 4 * sigma/sqrt(n),
                length.out = 100), muA + 4 * sigma/sqrt(n))), c(0, dnorm(seq(mu0 -
                qnorm(1 - alpha/2) * sigma/sqrt(n), to = muA + 4 * sigma/sqrt(n),
                length.out = 100), mean = muA, sd = sigma/sqrt(n)), 0), border = "black",
                col = "grey")
        }
    }

    return(length(p[p >= alpha])/k)
}
```